# HsdMSR KO

We analyze the 6mA sites 0104 in this notebook

First, we need to have all the datas

## Load Data of MU
```{R}
rm(list=ls())
library(tidyr)
library(data.table)
library(dplyr)


## defeine a fuction to normalize the OriginalValue
## yi = (xi - min(x)) / (max(x) - min(x))
get.normalized <- function(df){
  eps <- 1e-6
  df$Value <- (df$OriginalValue - min(df$OriginalValue))/(max(df$OriginalValue) - min(df$OriginalValue)) * (1 - 2 * eps) + eps
  return(df)
}

get.chromosome.name <- function(df){
  df$Chromosome <- gsub("refseq\\|NC_005773\\.3\\|chromosome","chromosome",df$Chromosome)
  df$Chromosome <- gsub("refseq\\|NC_007275\\.1\\|small","small.plasmid",df$Chromosome)
  df$Chromosome <- gsub("refseq\\|NC_007274\\.1\\|large","large.plasmid",df$Chromosome)
  return(df)
}

# This one for mCaller_MU
get.chromosome.name2 <- function(df){
  df$Chromosome <- gsub("small","small.plasmid",df$Chromosome)
  df$Chromosome <- gsub("large","large.plasmid",df$Chromosome)
  return(df)
}

# load files
# all Asites in 1448A
Asites <- fread("/Users/lubeifang/Desktop/Benchmark/DATA/1448AWT/1448A_Asite.bed", header = F)
Asites <- Asites[,c(1,3,6)]
colnames(Asites) <- c("Chromosome","Position","Strand")
Asites <- get.chromosome.name(Asites)

# all 1448A motifs
motif1 <- read.csv("/Users/lubeifang/Desktop/Benchmark/DATA/1448AWT/1448A_CAGCN6CTC.bed", sep = "\t", header = F)
motif2 <- read.csv("/Users/lubeifang/Desktop/Benchmark/DATA/1448AWT/1448A_GAGN6GCTG.bed", sep = "\t", header = F)
# Type1 motif
MotifT1_peak <- rbind(motif1, motif2)
MotifT1 <- MotifT1_peak[,c(1,3,6)]
colnames(MotifT1) <- c("Chromosome","Position","Strand")
MotifT1 <- get.chromosome.name(MotifT1)
# Type2 motif
MotifT2_peak <- read.csv("/Users/lubeifang/Desktop/Benchmark/DATA/1448AWT/1448A_RAGTACTY.bed", sep = "\t", header = F)
MotifT2 <- MotifT2_peak[,c(1,3,6)]
colnames(MotifT2) <- c("Chromosome","Position","Strand")
MotifT2 <- get.chromosome.name(MotifT2)
# ALL motifs
Motifs <- rbind(motif1, motif2, MotifT2_peak)
Motifs <- Motifs[,c(1,3,6)]
colnames(Motifs) <- c("Chromosome","Position","Strand")
Motifs <- get.chromosome.name(Motifs)

# SMRT_MU from PacBio
SMRT_WT = fread("/Users/lubeifang/Desktop/Benchmark/DATA/1448AWT/smrt.bed", sep = "\t", header = F,skip = 1)
SMRT_KO = fread("/Users/lubeifang/Desktop/Benchmark/DATA/0104KO/smrt.bed", sep = "\t", header = F,skip = 1)
SMRT_MU <- semi_join(SMRT_WT, SMRT_KO, by = c("V1", "V5", "V7"))
rm(SMRT_WT, SMRT_KO)

SMRT_MU <- SMRT_MU[,c(1,5,7,6)]
colnames(SMRT_MU) <- c("Chromosome","Position","Strand","OriginalValue")
SMRT_MU <- arrange(SMRT_MU, desc(OriginalValue)) %>%
  mutate(Rank = row_number())%>%
  get.normalized()%>%
  get.chromosome.name()
# Tombo direct 
Tombo_denovo_MU = fread("/Users/lubeifang/Desktop/Benchmark/DATA/0104KO/tombo_denovo.bed", sep="\t", header = T)
Tombo_denovo_MU <- Tombo_denovo_MU[,c(1,3,6,7)]
colnames(Tombo_denovo_MU) <- c("Chromosome","Position","Strand","OriginalValue")
Tombo_denovo_MU <- arrange(Tombo_denovo_MU, desc(OriginalValue)) %>%
  mutate(Rank = row_number()) %>%
  get.normalized()%>%
  get.chromosome.name()
#Tombo_denovo_MU$Value <- round(Tombo_denovo_MU$OriginalValue,6)
# Tombo level_compare
Tombo_levelcom_MU = fread("/Users/lubeifang/Desktop/Benchmark/DATA/0104KO/tombo_levelcom.bed", sep="\t", header = T)
Tombo_levelcom_MU <- Tombo_levelcom_MU[, c(1,3,6,7)] # this OriginalValue is -log(p-OriginalValue)
colnames(Tombo_levelcom_MU) <- c("Chromosome","Position","Strand","OriginalValue")
Tombo_levelcom_MU <- arrange(Tombo_levelcom_MU, desc(OriginalValue)) %>%
  mutate(Rank = row_number()) %>%
  get.normalized()%>%
  get.chromosome.name()
#Tombo_levelcom_MU$OriginalValue <- round(Tombo_levelcom_MU$OriginalValue,1)
# Tombo model_compare to WGA
Tombo_modelcom_MU = fread("/Users/lubeifang/Desktop/Benchmark/DATA/0104KO/tombo_modelcom.bed", sep="\t", header = T)
Tombo_modelcom_MU <- Tombo_modelcom_MU[, c(1,3,6,7)]
colnames(Tombo_modelcom_MU) <- c("Chromosome","Position","Strand","OriginalValue")
Tombo_modelcom_MU <- arrange(Tombo_modelcom_MU, desc(OriginalValue)) %>%
  mutate(Rank = row_number()) %>%
  get.normalized()%>%
  get.chromosome.name()
# Tombo_modelcom_MU$OriginalValue <- round(Tombo_modelcom_MU$OriginalValue,3)
# mCaller_MU 
mCaller_MU = fread("/Users/lubeifang/Desktop/Benchmark/DATA/0104KO/mcaller.bed", sep="\t", header = F)
mCaller_MU <- mCaller_MU[,c(1,3,6,5)]
colnames(mCaller_MU) <- c("Chromosome","Position","Strand","OriginalValue")
mCaller_MU <- arrange(mCaller_MU, desc(OriginalValue)) %>%
  mutate(Rank = row_number())%>%
  get.normalized() %>%
  get.chromosome.name2()
# Nanodisco_MU
Nanodisco_MU = fread("/Users/lubeifang/Desktop/Benchmark/DATA/0104KO/Nanodisco.csv", header = T)
Nanodisco_MU <- drop_na(Nanodisco_MU)
Nanodisco_MU$Strand <- ifelse(Nanodisco_MU$dir == "fwd", "+", "-")
Nanodisco_MU <- Nanodisco_MU[,c(1,2,10,8)] # The OriginalValue is t-test p-OriginalValue
colnames(Nanodisco_MU) <- c("Chromosome","Position","Strand","OriginalValue")
Nanodisco_MU$OriginalValue <- -log10(Nanodisco_MU$OriginalValue)
Nanodisco_MU <- arrange(Nanodisco_MU, desc(OriginalValue)) %>%
  mutate(Rank = row_number())%>%
  get.normalized()%>%
  get.chromosome.name()
# Dorado_MU+Modkit
Dorado_MU = fread("/Users/lubeifang/Desktop/Benchmark/DATA/0104KO/dorado.bed", header = F)
Dorado_MU <- Dorado_MU[,c(1,3,6,11)]
colnames(Dorado_MU) <- c("Chromosome","Position","Strand","OriginalValue")
Dorado_MU <- arrange(Dorado_MU, desc(OriginalValue)) %>%
  mutate(Rank = row_number())%>%
  get.normalized()%>%
  get.chromosome.name()
# hmmaerhead
Hammerhead_MU = fread("/Users/lubeifang/Desktop/Benchmark/DATA/0104KO/hammerhead.txt", sep="\t", header = TRUE)
Hammerhead_MU <- rbind(data.frame(Strand = "+", as.data.frame(Hammerhead_MU)),
                    data.frame(Strand = "-", as.data.frame(Hammerhead_MU)))
Hammerhead_MU <- Hammerhead_MU[,c(2,3,1,4)]
colnames(Hammerhead_MU) <- c("Chromosome","Position","Strand","OriginalValue")
Hammerhead_MU <- arrange(Hammerhead_MU, desc(OriginalValue)) %>%
  mutate(Rank = row_number())%>%
  get.normalized()%>%
  get.chromosome.name()
```

###Plot distribution of Value
```{R}
data.1448AMU <- rbind(data.frame(Category = 'Tombo_denovo', as.data.frame(Tombo_denovo_MU)),
                      data.frame(Category = 'Tombo_levelcom', as.data.frame(Tombo_levelcom_MU)),
                      data.frame(Category = 'Tombo_modelcom', as.data.frame(Tombo_modelcom_MU)),
                      data.frame(Category = 'mCaller', as.data.frame(mCaller_MU)),
                      data.frame(Category = 'Nanodisco', as.data.frame(Nanodisco_MU)),
                      data.frame(Category = 'Dorado', as.data.frame(Dorado_MU)),
                      data.frame(Category = 'Hammerhead', as.data.frame(Hammerhead_MU))) %>%
  drop_na()


library(ggridges)
library(hrbrthemes)
p2 <- ggplot(data.1448AMU, aes(x=Value, y=Category, fill=Category)) +
  geom_density_ridges(color = NA) +
  theme_ridges() + 
  scale_fill_manual(values = c("#98B85D","#7262AC","#AC667E","#287c9e","#BDA96F","#a9a9a9","#e29578"))+
  theme_ipsum() +
  ylab("Density") +
  xlab("Assigned Fraction Probability") +
  ggtitle("1448A ΔHsdMSR Assigned Fraction Distribution") +
  theme(legend.position = "none")

ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/distribution/1448AMU.pdf", width = 8, height = 6, font="Arial")

rm(data.1448AMU)
```

## Load Data of WGA
```{R}
# Tombo_levelcom
Tombo_levelcom_WGA = fread("/Users/lubeifang/Desktop/Benchmark/DATA/1448AWGA/1448AWGA_levelcom.bed", sep="\t", header = TRUE)
Tombo_levelcom_WGA <- Tombo_levelcom_WGA[, c(1,3,6,7)]
colnames(Tombo_levelcom_WGA) <- c("Chromosome","Position","Strand","OriginalValue")
Tombo_levelcom_WGA <- arrange(Tombo_levelcom_WGA, desc(OriginalValue)) %>%
  mutate(Rank = row_number())%>%
  get.normalized()%>%
  get.chromosome.name()

# Tombo model_compare 
Tombo_modelcom_WGA = fread("/Users/lubeifang/Desktop/Benchmark/DATA/1448AWGA/1448AWGA_modelcom.bed", sep="\t", header = TRUE)
Tombo_modelcom_WGA <- Tombo_modelcom_WGA[, c(1,3,6,7)]
colnames(Tombo_modelcom_WGA) <- c("Chromosome","Position","Strand","OriginalValue")
Tombo_modelcom_WGA <- arrange(Tombo_modelcom_WGA, desc(OriginalValue)) %>%
  mutate(Rank = row_number())%>%
  get.normalized()%>%
  get.chromosome.name()

# Nanodisco
Nanodisco_WGA = fread("/Users/lubeifang/Desktop/Benchmark/DATA/1448AWGA/1448AWGA_nanodisco.csv", header = TRUE)
Nanodisco_WGA <- drop_na(Nanodisco_WGA)
Nanodisco_WGA$Strand <- ifelse(Nanodisco_WGA$dir == "fwd", "+", "-")
Nanodisco_WGA <- Nanodisco_WGA[,c(1,2,10,8)]
colnames(Nanodisco_WGA) <- c("Chromosome","Position","Strand","OriginalValue")
Nanodisco_WGA$OriginalValue <- -log10(Nanodisco_WGA$OriginalValue)
Nanodisco_WGA <- arrange(Nanodisco_WGA, desc(OriginalValue)) %>%
  mutate(Rank = row_number())%>%
  get.normalized()%>%
  get.chromosome.name()

# Here are singel mode, we need WT and 0104 data of them.
# WT
# Tombo direct 
Tombo_denovo_WGA = fread("/Users/lubeifang/Desktop/Benchmark/DATA/1448AWGA/1448AWGA_de_novo.bed", sep="\t", header = TRUE)
Tombo_denovo_WGA <- Tombo_denovo_WGA[,c(1,3,6,7)]
colnames(Tombo_denovo_WGA) <- c("Chromosome","Position","Strand","OriginalValue")
Tombo_denovo_WGA <- arrange(Tombo_denovo_WGA, desc(OriginalValue)) %>%
  mutate(Rank = row_number()) %>%
  get.normalized()%>%
  get.chromosome.name()
# mCaller 
mCaller_WGA = fread("/Users/lubeifang/Desktop/Benchmark/DATA/1448AWGA/1448AWGA_mCaller.bed", sep="\t", header = F)
mCaller_WGA <- mCaller_WGA[,c(1,3,6,5)]
colnames(mCaller_WGA) <- c("Chromosome","Position","Strand","OriginalValue")
mCaller_WGA <- arrange(mCaller_WGA, desc(OriginalValue)) %>%
  mutate(Rank = row_number())%>%
  get.normalized()%>%
  get.chromosome.name2()
# Dorado+Modkit
Dorado_WGA = fread("/Users/lubeifang/Desktop/Benchmark/DATA/1448AWGA/1448AWGA_Dorado.bed", header = F)
Dorado_WGA <- Dorado_WGA[,c(1,3,6,11)]
colnames(Dorado_WGA) <- c("Chromosome","Position","Strand","OriginalValue")
Dorado_WGA <- arrange(Dorado_WGA, desc(OriginalValue)) %>%
  mutate(Rank = row_number())%>%
  get.normalized()%>%
  get.chromosome.name()

# hmmaerhead
Hammerhead_WGA = fread("/Users/lubeifang/Desktop/Benchmark/DATA/1448AWGA/1448AWGA_hammerhead.txt", sep="\t", header = TRUE)
Hammerhead_WGA <- rbind(data.frame(Strand = "+", as.data.frame(Hammerhead_WGA)),
                        data.frame(Strand = "-", as.data.frame(Hammerhead_WGA)))
Hammerhead_WGA <- Hammerhead_WGA[,c(2,3,1,4)]
colnames(Hammerhead_WGA) <- c("Chromosome","Position","Strand","OriginalValue")
Hammerhead_WGA <- arrange(Hammerhead_WGA, desc(OriginalValue)) %>%
  mutate(Rank = row_number())%>%
  get.normalized()%>%
  get.chromosome.name()


rm(get.chromosome.name, get.chromosome.name2, get.normalized)
```

Then, we call the motifs.
## MEME_motifs
```{r}
library(memes)
library(seqinr)
library(GenomicRanges)
library(rtracklayer)
library(magrittr)
library(universalmotif)
library(Biostrings)
library(BSgenome)
library(ggplot2)
library(tidyr)
library(gridExtra)
# load fastq file and make it into stringset, ready for get_sequence
fasta_file <- "/Users/lubeifang/Desktop/BIOTOOLS/ref/1448A_formeme.fasta"
psph_stringset <- readDNAStringSet(fasta_file)

# define how to meme search
# We can change the batch search size for fasta and meme search way
get.meme <- function(sorted){
    sorted <- sorted[sorted$Position >= 20, ]
    bed <- data.frame(chr=sorted$Chromosome,
                      start=sorted$Position-1,
                      end=sorted$Position,
                      Starnd=sorted$Strand)
    gR <- GRanges(seqnames = bed$chr,
                  ranges = IRanges(start = bed$start, end = bed$end),
                  strand = "*")
    # resize ranges
    gRr <- resize(gR,40, "center") 
    sequences <- get_sequence(gRr, psph_stringset)
    # unique(width(gRr))
    # s <- data.frame(sequences)
  meme_results <- runStreme(sequences,control = "shuffle", minw = 8, maxw=10, nmotifs = 6)
  return(meme_results)
}


# Do the MEME
# set how many sites we would like to include
top = 10000
plot_list <- list()
meme_results.df <- data.frame()
top10k.df <- data.frame()
dataset.name <- c("SMRT", "Tombo_levelcom", "Tombo_modelcom", "Nanodisco", "Tombo_denovo", "mCaller", "Dorado","Hammerhead")
#dataset.name <- c("Dorado","Hammerhead")
for (i in dataset.name){
  print(i) 
#  i = "Hammerhead"
  file <- get(paste0(i,"_MU"))
  if (i == "mCaller" | i == "Dorado"){
    sorted1 <- file[order(file$Value, decreasing = T),][1:top,] # bigger to smaller
  }
  else{
    sorted1 <- inner_join(file, Asites, by = c("Chromosome","Position","Strand"))
    # Order it by Value, and get first top sites file
    sorted1 <- file[order(file$Value, decreasing = T),][1:top,] # bigger to smaller
  }
  sorted1 <- drop_na(sorted1) # SMRT for 0104LOSS have only 2873 rows
  
  # did this after peaks annotation, this only considered chromosome one.
#  temp <- data.frame(name = i, data.frame(inner_join(motif.peak.df, sorted1[sorted1$Chromosome=="chromosome"],
#                                                        by = c("Position"))))
  top10k.df <- rbind(top10k.df, data.frame(name = i, data.frame(sorted1)))
  
  meme_results <- get.meme(sorted1)
  meme_results.df <- rbind(meme_results.df, as.data.frame(Tool = i, data.frame(meme_results)))
  plot <- meme_results %>%
    to_list() %>%
    view_motifs()
  name=paste0(i,"_",top,"motif")
  plot <- plot + ggtitle(name)
  plot_list[[length(plot_list) + 1]] <- plot
}

# plot <- meme_results.df %>% 
#   to_list() %>% 
#   view_motifs()

g <- arrangeGrob(grobs = plot_list, nrow=2) 
ggsave(file="1448AMU_10000_6motifs.pdf", path = "/Users/lubeifang/Desktop/Benchmark/Figure/F2_table2motif/",g, width = 32, height = 18)

# to_list(meme_results.df)
motif_detail <- meme_results.df[,c(-1,-17)]
write.csv(motif_detail,"/Users/lubeifang/Desktop/Benchmark/Figure/F2_table2motif/1448AMU_10k_6motifs_memeresults.csv")
rm(get.meme)


count_data <- aggregate(Position ~ name + Chromosome + Strand, data = top10k.df, FUN = length)

ggplot(count_data[count_data$name!="SMRT",], aes(x=name, y=Position, fill=Chromosome)) +   
#ggplot(count_data[count_data$name!="SMRT",], aes(x=name, y=Position, fill=Strand)) + 
  geom_bar(position="stack", stat = "identity") +
#  scale_fill_manual(values = c("#E7BCC6","#FDCF9E"))+
  scale_fill_manual(values = c("#8A8DBF","#E7BCC6","#FDCF9E"))+
  theme_classic()+
  theme(axis.text.y = element_blank()) +
  theme(axis.text.x =element_text(angle =90,hjust = 1,vjust = 0.5)) +
  ylab("Counts") +
  xlab("") +
  ggtitle("1448AMU Chromosome distribution of Top 10k sites predicted by each tools")

ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/distribution/1448AMU_top10kdistri_chr.pdf", width = 8, height = 6, font="Arial")
```

### top 10k peaks
```{R}
library(ChIPseeker)
library(ChIPpeakAnno)
library(clusterProfiler)
require(GenomicFeatures)
library(GenomicRanges)

# load annotation
ps_txdb <- makeTxDbFromGFF("/Users/lubeifang/Desktop/BIOTOOLS/ref/CHIPPEAKANNO/1448A_peak.gff")
annoData <- toGRanges(ps_txdb, feature="gene")

# Only consider Chromosome here
top10k.peak = data.frame()
dataset.name <- c("Tombo_levelcom", "Tombo_modelcom", "Nanodisco", "Tombo_denovo", "mCaller", "Dorado","Hammerhead")
for (i in dataset.name){
  print(i)
  peak <- top10k.df[top10k.df$Chromosome == "chromosome" & top10k.df$name == i,]
  peak_gr <- GRanges(seqnames="chr1",
                   ranges=IRanges(start=as.numeric(as.matrix(peak[,3]-1)),
                                  end= as.numeric(as.matrix(peak[,3])),
                                  names=as.matrix(as.matrix(peak[,1]))))
  annotatedpeak <- annotatePeakInBatch(peak_gr, AnnotationData=annoData)
  top10k.peak = rbind(top10k.peak, data.frame(Tool = i, as.data.frame(annotatedpeak)))
}


colnames(top10k.peak)
temp <- top10k.peak[,c(1,13)]

# count how many sites of each tools got
count_data <- aggregate(distancetoFeature ~ Tool, data = temp, FUN = length)

ggplot(temp, aes(x=distancetoFeature, group=Tool, fill=Tool)) +
  geom_histogram(alpha = 0.6, binwidth = 30, color = "#CFCFE5") +
#  geom_density(alpha = 0.6, color = NA) +
  theme_bw() +
  facet_wrap(~Tool, nrow = 2) +
  theme(
    legend.position = "none",
    legend.title = element_blank(),
    axis.text.x = element_text(family="Arial", size = 6),
    axis.text.y = element_text(family="Arial", size = 12),
    axis.title.x = element_text(family="Arial", size = 12),
    axis.title.y = element_text(family="Arial", size = 12),
    strip.background = element_rect(colour="black", fill="#C6AEBA")) +
#  scale_fill_manual(values = c("#98B85D","#AC667E")) +
  xlab("Distance to Start Codon") +
  ylab("Count") +
  ggtitle("MU Top 10k sites distribution of start codon in 1448A") +
  geom_text(data = count_data, aes(label = paste("Sites number : ",distancetoFeature), x = Inf, y = Inf), hjust = 1.05, vjust = 1.5, size = 3, color = "black") +
  xlim(-1000,2000)

ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/distribution/1448AMU_top10kdistri_start.pdf", width = 10, height = 6, font="Arial")
```

### motif enrich sites and pvalue
```{R}
motif_detail
dataset.name <- c("Tombo_levelcom", "Tombo_modelcom", "Nanodisco", "Tombo_denovo", "mCaller", "Dorado","Hammerhead")
tool_detail <- data.frame(name=rep(c("SMRT", "Tombo_levelcom", "Tombo_modelcom", "Nanodisco", "Tombo_denovo", "mCaller", "Dorado","Hammerhead"),1),
                          type=c(rep(c("Type 2 Motif"),8)),
                          nsites=as.numeric(c("267","1459","995","539","0","0","61","1598")),
                          pval=as.numeric(c("0.00044","2.3e-11","1.2e-6","2.1e-6","0","0","0.031","0.013")))

tool_detail<-subset(tool_detail, name!="SMRT")
tool_detail$pval <- round(-log(tool_detail$pval,10),2)
tool_detail[tool_detail=="Inf"] <- "0"
tool_detail$pval <- as.numeric(tool_detail$pval)

ggplot() +
  geom_point(data = tool_detail, aes(x = name, y = nsites), color = "#AC667E", size = 4) +
  geom_line(data = tool_detail, aes(x = name, y = nsites, group = type), color = "grey") +
  theme_bw() +
  theme(axis.text.x = element_text(family="Arial", size = 10, angle = 90),
        axis.text.y = element_text(family="Arial", size = 10)) +
  xlab("") +
  ylab("Motif enriched sites")

ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/F2_table2motif/1448AMU_moitf_nsite.pdf", width = 7, height = 5, font="Arial")

ggplot() +
  geom_point(data = tool_detail, aes(x = name, y = pval), color = "#AC667E", size = 4) +
  geom_line(data = tool_detail, aes(x = name, y = pval, group = type), color = "grey") +
  theme_bw() +
  theme(axis.text.x = element_text(family="Arial", size = 10, angle = 90),
        axis.text.y = element_text(family="Arial", size = 10)) +
  xlab("") +
  ylab("Motif enriched -log(p-value)")

ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/F2_table2motif/1448AMU_moitf_pval.pdf", width = 7, height = 5)

```

We will focus on the sites then

## Sites comparison
### functions define
#### 5mer-shift
```{r}
# define two functions
# get a 5-mer of SMRT position
get.5mer.df <- function(df){
  df1 <- df
  df1$Position <- df1$Position + 1
  df2 <- df
  df2$Position <- df2$Position + 2
  df3 <- df
  df3$Position <- df3$Position - 1
  df4 <- df
  df4$Position <- df4$Position - 2
  df5 <- rbind(df1,df2,df3,df4,df) %>%
    arrange(desc(OriginalValue)) %>%
    distinct(Position,Strand,Chromosome, .keep_all = T)
  return(df5)
}


```

####get.trim.df.A
```{R}
# Compare to groundtruth
# 1448A chromosome, large plasmid and small plasmid have 1.22e7 nt in both strands
# 1448A chromosome, large plasmid and small plasmid have 2.6e6 A in both strands

# for mCaller, Dorado, they are singel mode and A only, so the don't need shift
get.trim.df.A <- function(preds_df, gt_df) {
  TP1 <- c()
  FN1 <- c() 
  FP1 <- c()
  TN1 <- c()
  TPR1 <- c()
  TNR1 <- c()
  FPR1 <- c()
  precision1 <- c()
  recall1 <- c()
  F1score1 <- c()
  rank1 <- c()
  originalvalue1 <- c()
  value1 <- c()
  
  cutoffs <- seq(log10(1), log10(2.573e6), length.out = 200) # for A
  cutoffs <- 10^cutoffs
  
  for (cutoff in cutoffs) {
    print(cutoff)
    preds <- subset(preds_df, Rank <= cutoff) # if it is rank, make sure <=; if it is fraction, make sure >=
    rank1 <- c(rank1,nrow(preds))
    value1 <- c(value1,min(preds$Value))
    originalvalue1 <- c(originalvalue1,min(preds$OriginalValue))
    intersection <- inner_join(preds, gt_df, by = c("Position", "Chromosome", "Strand"))
    TP <- nrow(intersection)
    TP1 <- c(TP1,TP)
    union <- rbind(preds,gt_df)
    union <- union[!duplicated(union[, c("Position", "Chromosome", "Strand")]), ]
    diff <- anti_join(Asites, union, by = c("Position", "Chromosome", "Strand"))
    TN <- nrow(diff)
    TN1 <- c(TN1,TN)
    FP = nrow(preds)-TP
    FP1 <- c(FP1,FP)
    FN = nrow(gt_df)-TP
    FN1 <- c(FN1,FN)
    precision = TP/nrow(preds)
    precision1 <- c(precision1, precision)
    recall = TP/nrow(gt_df)
    recall1 <- c(recall1, recall)
    F1score = 2*precision*recall/(precision+recall)
    F1score1 <- c(F1score1,F1score)
    TPR1 <- c(TPR1, TP/(TP+FN))
    TNR1 <- c(TNR1, TN/(TN+FP))
    FPR1 <- c(FPR1, FP/(FP+TN))
  }
  plot1 <- data.frame(Cutoff = cutoffs, Rank = rank1, Value = value1, OriginalValue = originalvalue1, TP = TP1, FN = FN1, FP = FP1, TN = TN1, Precision = precision1, Recall = recall1, F1score = F1score1, TPR = TPR1, TNR = TNR1, FPR = FPR1) 
  return(plot1)
} 

```

####get.trim.df.ATCG
```{R}
# For ATCG tools
get.trim.df.ATCG <- function(preds_df, gt_df) {
  
  gt_df_5mer <- get.5mer.df(gt_df)
  
  TP1 <- c()
  FN1 <- c() 
  FP1 <- c()
  TN1 <- c()
  TPR1 <- c()
  TNR1 <- c()
  FPR1 <- c()
  precision1 <- c()
  recall1 <- c()
  F1score1 <- c()
  rank1 <- c()
  originalvalue1 <- c()
  value1 <- c()
  
  cutoffs <- seq(log10(1), log10(1.223e7), length.out = 200) # for ATCG
  cutoffs <- 10^cutoffs
  
  for (cutoff in cutoffs) {
    print(cutoff)
    preds <- subset(preds_df, Rank <= cutoff) # if it is rank, make sure <=; if it is fraction, make sure >=
    rank1 <- c(rank1,nrow(inner_join(preds, Asites, by = c("Chromosome","Position","Strand"))))
    value1 <- c(value1,min(preds$Value))
    originalvalue1 <- c(originalvalue1,min(preds$OriginalValue))

    intersection1 <- inner_join(preds, gt_df_5mer, by = c('Position','Chromosome','Strand'))
    TP_precision = nrow(intersection1)
    TP1 <- c(TP1,TP_precision)
    union <- rbind(preds,gt_df)
    union <- union[!duplicated(union[, c("Position", "Chromosome", "Strand")]), ]
    diff <- anti_join(Asites, union, by = c("Position", "Chromosome", "Strand"))
    TN <- nrow(diff)
    TN1 <- c(TN1,TN)
    FP = nrow(preds)-TP_precision
    FP1 <- c(FP1,FP)
    
    union <- rbind(preds,gt_df)
    union <- union[!duplicated(union[, c("Position", "Chromosome", "Strand")]), ]
    diff <- anti_join(Asites, union, by = c("Position", "Chromosome", "Strand"))
    TN <- nrow(diff)
    TN1 <- c(TN1,TN)
    
    b <- get.5mer.df(preds)
    intersection2 <- inner_join(b, gt_df, by = c('Position','Chromosome','Strand'))
    TP_recall = nrow(intersection2)
    FN = nrow(gt_df)-TP_recall
    FN1 <- c(FN1,FN)
    
    precision = TP_precision/nrow(preds)
    precision1 <- c(precision1, precision)
    recall = TP_recall/nrow(gt_df)
    recall1 <- c(recall1, recall)
    F1score = 2*precision*recall/(precision+recall)
    F1score1 <- c(F1score1,F1score)
    TPR1 <- c(TPR1, TP_precision/(TP_precision+FN))
    TNR1 <- c(TNR1, TN/(TN+FP))
    FPR1 <- c(FPR1, FP/(FP+TN))
  }
  plot1 <- data.frame(Cutoff = cutoffs, Rank = rank1, Value = value1, OriginalValue = originalvalue1, TP = TP1, FN = FN1, FP = FP1, TN = TN1, Precision = precision1, Recall = recall1, F1score = F1score1, TPR = TPR1, TNR = TNR1, FPR = FPR1) 
  return(plot1)
} 

```

Get trimed.df and draw F1 score
### trimed.df calculated
```{r}
# dataset.name <- c("Tombo_levelcom", "Tombo_modelcom", "Nanodisco", "Tombo_denovo", "mCaller", "Dorado", "Hammerhead")
dataset.name <- c("Tombo_levelcom", "Tombo_modelcom", "Tombo_denovo", "mCaller", "Dorado")
trimed.df <- data.frame()
for (name in dataset.name){
  print(name)
  df <- get(paste0(name,"_MU"))
  # single mode
  if (name == "Dorado" | name == "mCaller"){
      # Tombo_denovo and Hammerhead, they are ATCG and single mode, shift and 1.2e7 cutoffs
    trimed_temp <-  get.trim.df.A(df, SMRT_MU)
    trimed.df <- rbind(trimed.df, data.frame(Tool = name, as.data.frame(trimed_temp)))
  }
  else{
    trimed_temp <-  get.trim.df.ATCG(df, SMRT_MU)
    trimed.df <- rbind(trimed.df, data.frame(Tool = name, as.data.frame(trimed_temp)))
  }
  rm(trimed_temp)
  trimed.df[is.na(trimed.df)] <- 0
}
  

write.csv(trimed.df,"/Users/lubeifang/Desktop/Benchmark/intermediateFILE/1448AMU.trimed.df0611.csv")

```

## plot figures
### F1 score
```{R}
library(gridExtra)
library(patchwork)

p <- ggplot(trimed.df, aes(x=Rank, y=F1score, group=Tool, color=Tool))+
  geom_line(size=0.8) +
  ggtitle("1448AMU F1 score") +
  theme_light() +
  xlab("A sites") +
  theme(
    panel.border = element_rect(color = "black", fill = NA),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_blank(),
    axis.text.x = element_text(family = "Arial", size = 10),
    axis.text.y = element_text(family = "Arial", size = 10),
    legend.position="none"
  ) +
  scale_color_manual(values = c("#98B85D","#7262AC","#AC667E","#287c9e","#BDA96F","#a9a9a9","#e29578"))


pp <- ggplot(trimed.df, aes(x=Rank, y=F1score, group=Tool, color=Tool))+
  geom_line(size=0.5) +
#  geom_point(size = 0.2, color = "grey") +
  theme_bw() +
  theme(legend.position="none")+
  scale_color_manual(values = c("#98B85D","#7262AC","#AC667E","#287c9e","#BDA96F","#a9a9a9","#e29578")) +
    xlim(0,20000)+
  xlab("")+
  ylab("")
p1 <- p + inset_element(pp, left = 0.3, bottom = 0.3, right = 0.95, top = 0.95) 
p1

ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/F3_trim/1448AMU_f1score0429.pdf", plot = p1, width = 7, height = 4.5)

p2<-ggplot(trimed.df, aes(x=Recall, y=Precision, group=Tool, color=Tool))+
  geom_line(size=0.8) +
  ggtitle("1448AMU PRC") +
  theme_light() +
  theme(
    panel.border = element_rect(color = "black", fill = NA),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_blank(),
    axis.text.x = element_text(family = "Arial", size = 10),
    axis.text.y = element_text(family = "Arial", size = 10),
    legend.position="none"
  ) +
  scale_color_manual(values = c("#98B85D","#7262AC","#AC667E","#287c9e","#BDA96F","#a9a9a9","#e29578"))
ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/F3_trim/1448AMU_PRC0429.pdf", p2,width = 7, height = 4.5)

p3<-ggplot(trimed.df, aes(x=FPR, y=TPR, group=Tool, color=Tool))+
  geom_line(size=0.8) +
  ggtitle("1448AMU ROC") +
  theme_light() +
    theme(
    panel.border = element_rect(color = "black", fill = NA),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_blank(),
    axis.text.x = element_text(family = "Arial", size = 10),
    axis.text.y = element_text(family = "Arial", size = 10),
    legend.position="none"
  )+
  scale_color_manual(values = c("#98B85D","#7262AC","#AC667E","#287c9e","#BDA96F","#a9a9a9","#e29578"))
ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/F3_trim/1448AMU_ROC0429.pdf", p3, width = 7, height = 4.5)

plot2 <- p1+p2+p3
ggsave("/Users/lubeifang/Desktop/Benchmark/Figure/F3_trim/1448AMU_alltools0429.pdf", plot2, width = 13, height = 4.3)
```
### Get the best F1 score
```{R}
dataset.name <- c("Tombo_levelcom", "Tombo_modelcom", "Nanodisco", "Tombo_denovo", "mCaller", "Dorado", "Hammerhead")
best.df <- data.frame()

# Give a dataframe of best F1 with cutoff
for (k in dataset.name){
  # Get the row of best F1 score
  df.cate <- subset(trimed.df, Tool == k)
  df.cate <- subset(df.cate,F1score == max(df.cate$F1score))
  best.df.temp <- df.cate[order(df.cate$OriginalValue, decreasing = F),][1,]
  best.df.temp <- cbind(Type = "BestF1", best.df.temp)
  best.df <- rbind(best.df, best.df.temp)
  # Get the row of best Recall score
  df.cate <- subset(trimed.df, Tool == k) 
  df.cate <- subset(df.cate,Recall == max(df.cate$Recall))
  best.df.temp <- df.cate[order(df.cate$Recall, decreasing = F),][1,]
  best.df.temp <- cbind(Type = "BestRecall", best.df.temp)
  best.df <- rbind(best.df, best.df.temp)
  # Get the row of best Precision score
  df.cate <- subset(trimed.df, Tool == k) 
  df.cate <- subset(df.cate,Precision == max(df.cate$Precision))
  best.df.temp <- df.cate[order(df.cate$Precision, decreasing = F),][1,]
  best.df.temp <- cbind(Type = "BestPrecision", best.df.temp)
  best.df <- rbind(best.df, best.df.temp)
}
rm(best.df.temp, df.cate)

write.csv(best.df,"/Users/lubeifang/Desktop/Benchmark/intermediateFILE/1448AMU.best.df0417.csv")
```

